Initial Analysis

### 2020-06-09 Scripts/Initial_Analysis.Rmd
Re-organized folders
Updates for submission
Re-organization of files

#### READ ME !!! ####
# Run this chunk before knit so you make sure you have all pkgs installed in R

ipak <- function(pkg){
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg)) 
    install.packages(new.pkg, dependencies = TRUE,repos = "http://cran.us.r-project.org")
  sapply(pkg, require, character.only = TRUE)
}

@@

ipak(packages)

ggtheme_map <- function(base_size = 9, Region = "NA") {

  theme(text             = element_text(#family = "Helvetica",
    color = "gray30", size = base_size),
    plot.title       = element_text(size = rel(1.25), hjust = 0, face = "bold"),
    panel.background = element_blank(),
    panel.border     = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(color = "transparent"),
    strip.background =element_rect(fill = "transparent"),
    strip.text.x = element_text(size = 18, colour = "black",face= "bold.italic", angle = 0),
    axis.line        = element_blank(), # element_line(colour = "grey30", size = .5))
    axis.ticks       = element_blank(),
    axis.text        = element_blank(),
    axis.title       = element_blank(),
    legend.key       = element_rect(colour = NA, fill = NA, size = 4),
    legend.position = "bottom",
    legend.key.width =unit(5,"line")
  )
}

ggtheme_plot <- function() {
  theme(
    plot.title = element_text(size = rel(1), hjust = 0, face = "bold"),
    panel.background = element_blank(),
    strip.background = element_blank(),
    # strip.text       = element_text(size = base_size, face = "italic"),
    panel.border     = element_blank(),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank(),
    axis.ticks = element_blank(),
    axis.text.x = element_text(size = 12,
                               angle = 0,
                               face = "plain"),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14),
    legend.key = element_rect(colour = NA, fill = NA),
    legend.position  = "right",
    legend.title = element_text(size = 14, face = "bold"),
    legend.text = element_text(size = 16),
    strip.text.x = element_text(size = 12, colour = "black", face = "bold"),
    strip.text = element_text(size = 12)
  )
}

@@

@@

@@

# Updates result's path for the jurisdiction
Results_Path <- paste(Results_Path,Jurisdiction,"/",sep="")

# Species list to get species names
Exploited_Species <- fread(paste(Data_Path,"Distribution_Data/Species/exploited_species_list.csv",sep="")) %>% 
  clean_names()

Species_Sampled <- fread(paste(Data_Path,"Distribution_Data/Sampled_Species.csv", sep =""))

Spp_Clasification <- fread(paste(Data_Path,"Distribution_Data/Species/SppTaxonName.csv",sep="")) %>% 
  clean_names()

# Spatial Data needed to remove duplicates
sau_eez_fes <- fread(paste(Data_Path,"Spatial_Data/sau_eez_fes.csv",sep="")) %>% 
  clean_names()

Clean_sau_eez_fes <- sau_eez_fes %>% 
  gather("Type","fishing_region",2,4) %>% 
  left_join(sau_eez_fes,
            by = ("fishing_entity_id")
  ) %>% 
  group_by(eez_name,fishing_entity,fishing_entity_id) %>% 
  summarise(n()) %>% 
  ungroup() %>% 
  ### Manually Fix names for estimating catch
  mutate(eez_name = ifelse(eez_name =="Greece (without Crete)","Greece",
                           ifelse(eez_name =="Greenland (Denmark)","Greenland",
                                  ifelse(eez_name =="United Kingdom (UK)","United Kingdom",
                                         ifelse(fishing_entity =="Italy","Italy",
                                                ifelse(eez_name =="Chile (mainland)","Chile",
                                                       ifelse(fishing_entity =="Brazil","Brazil",
                                                              ifelse(eez_name == "Ecuador (mainland)", "Ecuador",
                                                                     ifelse(eez_name =="Portugal (mainland)","Portugal",
                                                                            ifelse(fishing_entity == "Korea (North)","Korea (North)",
                                                                                   paste(eez_name))
                                                                     )
                                                              )
                                                       )))))),
         fishing_entity = ifelse(fishing_entity == "Viet Nam","Vietnam",fishing_entity
         )
  )

# UN Regions dataset
UN_Regions <- read.csv(paste(Data_Path,"Spatial_Data/UN_Regions.csv",sep=""), header = TRUE) %>% 
  clean_names() %>% 
  group_by(fishing_entity = country_or_area,
           georegion = region_name,
           sub_region = sub_region_name) %>% 
  summarise(n=n()) %>% #merge china's 3 rows
  select(-n) %>% 
  filter(fishing_entity != "") %>%  # there are three rows with "developing" status as in, the code
  ungroup() %>% 
  # Change names to match SAU data and for shorter versions
  mutate(
    fishing_entity = gsub("\\s*\\([^\\)]+\\)","",fishing_entity),
    fishing_entity = gsub("United Kingdom of Great Britain and Northern Ireland","United Kingdom",fishing_entity),
    fishing_entity = gsub( "United States of America", "USA",fishing_entity),
    fishing_entity = gsub("Democratic People's Republic of Korea", "Korea (North)",fishing_entity),
    fishing_entity = gsub("Republic of Korea", "Korea (South)",fishing_entity),
    fishing_entity = gsub("Iran (Islamic Republic of)", "Iran",fishing_entity),
    fishing_entity = gsub("Democratic Republic of the Congo", "Congo (ex-Zaire)",fishing_entity),
    # fishing_entity = gsub("Congo", "Congo, R. of",fishing_entity),
    fishing_entity = gsub("United Republic of Tanzania", "Tanzania",fishing_entity),
    fishing_entity = gsub("Cabo Verde", "Cape Verde",fishing_entity),
    fishing_entity = gsub("Timor-Leste", "Timor Leste",fishing_entity),
    fishing_entity = gsub(" and ", " & ",fishing_entity),
    # fishing_entity = gsub("Puerto Rico (USA)", "Puerto Rico",fishing_entity),
    fishing_entity = gsub("Taiwan", "Taiwan (China)",fishing_entity),
    fishing_entity = gsub("Côte d’Ivoire", "Côte d'Ivoire",fishing_entity),
    # fishing_entity = gsub("Russian Federation", "Russia",fishing_entity)
    fishing_entity = gsub("Viet Nam", "Vietnam",fishing_entity),
    fishing_entity = gsub("Solomon Islands", "Solomon Isl.",fishing_entity),
    fishing_entity = gsub("Marshall Islands", "Solomon Isl.",fishing_entity),
  )

# Manually change congo
UN_Regions[52,1] <- "Congo, R. of"

# Load Land shapefile
path_world_land <- paste(Data_Path,"Spatial_Data/ne_50m_admin_0_countries",sep="")

@@

@@

# View(unique(World_sf$eez_name))

@@

# Read Sau Value Data (Thank you Tim!)
SAU_Tim_Data <- fread(paste(Data_Path,"Distribution_Data/sau_catch_value_country_taxon_JEPA.csv", sep =""))

@@

# Read Species Status Data (Sub-routine Species Status)
Status_Data <- fread(paste(Results_Path,"Species_Status.csv", sep ="")) %>% 
  clean_names() %>% 
  rename(eez_name=territory)

@@

Clean_Results_Trans <- fread(paste(Data_Path,"Results/EEZ/Clean_Results_Trans.csv", sep =""))

>>>>

#### READ ME !!! ####
library(MyFunctions)

@@

my_lib(packages)

@@

### Clean names table

Create a table that matches all names

```{r names_table, eval =F, echo =F}

Clean_sau_eez_fes <- sau_eez_fes %>% 
  gather("Type","fishing_region",2,4) %>% 
  left_join(sau_eez_fes,
            by = ("fishing_entity_id")
  ) %>% 
  group_by(eez_name,fishing_entity,fishing_entity_id) %>% 
  summarise(n()) %>% 
  ungroup() %>% 
  ### Manually Fix names for estimating catch
  mutate(sf_eez_name = ifelse(eez_name =="Greece (without Crete)","Greece", # Vicky
                              ifelse(eez_name =="Greenland (Denmark)","Greenland",
                                     ifelse(eez_name =="United Kingdom (UK)","United Kingdom",
                                            ifelse(fishing_entity =="Italy","Italy",
                                                   ifelse(eez_name =="Chile (mainland)","Chile",
                                                          ifelse(fishing_entity =="Brazil","Brazil",
                                                                 ifelse(eez_name == "Ecuador (mainland)", "Ecuador",
                                                                        ifelse(eez_name =="Portugal (mainland)","Portugal",
                                                                               ifelse(fishing_entity == "Korea (North)","Korea (North)",
                                                                                      ifelse(fishing_entity == "Guadeloupe  (France)","Guadeloupe (France)",
                                                                                             ifelse(eez_name == "South Africa (Atlantic and Cape)","South Africa (Atlantic Coast)",
                                                                                                    ifelse(eez_name =="Viet Nam","Vietnam",
                                                                                                           ifelse(eez_name =="US Virgin Isl.","US Virgin Islands",
                                                                                                                  ifelse(eez_name == "Spain (mainland, Med and Gulf of Cadiz)", "Spain (Mediterranean and Gulf of Cadiz)",
                                                                                                                         paste(eez_name)
                                                                                                                  )
                                                                                                           )
                                                                                                    )
                                                                                             ))))))))))
  ),	
  fishing_entity = ifelse(fishing_entity == "Viet Nam","Vietnam",fishing_entity
  )
  )

# UN Regions dataset
UN_Regions <- read.csv(paste(my_path("D"),"Spatial/UN_Regions.csv",sep=""), header = TRUE) %>% 
  clean_names() %>% 
  mutate(un_fishing_entity = country_or_area) %>% 
  group_by(un_fishing_entity,
           fishing_entity = country_or_area,
           georegion = region_name,
           sub_region = sub_region_name) %>% 
  summarise(n=n()) %>% #merge china's 3 rows
  select(-n) %>% 
  filter(fishing_entity != "") %>%  # there are three rows with "developing" status as in, the code
  ungroup() %>% 
  # Change names to match SAU data and for shorter versions
  mutate(
    fishing_entity = gsub("\\s*\\([^\\)]+\\)","",fishing_entity),
    fishing_entity = gsub("Curaçao","Curacao",fishing_entity),
    fishing_entity = gsub("United Kingdom of Great Britain and Northern Ireland","United Kingdom",fishing_entity),
    fishing_entity = gsub( "United States of America", "USA",fishing_entity),
    fishing_entity = gsub("Democratic People's Republic of Korea", "Korea (North)",fishing_entity),
    fishing_entity = gsub("Republic of Korea", "Korea (South)",fishing_entity),
    fishing_entity = gsub("Iran (Islamic Republic of)", "Iran",fishing_entity),
    fishing_entity = gsub("Democratic Republic of the Congo", "Congo (ex-Zaire)",fishing_entity),
    # fishing_entity = gsub("Congo", "Congo, R. of",fishing_entity),
    fishing_entity = gsub("United Republic of Tanzania", "Tanzania",fishing_entity),
    fishing_entity = gsub("Cabo Verde", "Cape Verde",fishing_entity),
    fishing_entity = gsub("Timor-Leste", "Timor Leste",fishing_entity),
    fishing_entity = gsub(" and ", " & ",fishing_entity),
    # fishing_entity = gsub("Puerto Rico (USA)", "Puerto Rico",fishing_entity),
    fishing_entity = gsub("Taiwan", "Taiwan (China)",fishing_entity),
    fishing_entity = gsub("Côte d’Ivoire", "Côte d'Ivoire",fishing_entity),
    # fishing_entity = gsub("Russian Federation", "Russia",fishing_entity)
    fishing_entity = gsub("Viet Nam", "Vietnam",fishing_entity),
    fishing_entity = gsub("Solomon Islands", "Solomon Isl.",fishing_entity),
    fishing_entity = gsub("Marshall Islands", "Solomon Isl.",fishing_entity),
  ) %>% 
  mutate(
    fishing_entity = ifelse(un_fishing_entity == "Congo","Congo, R. of",
                            ifelse(un_fishing_entity == "Democratic Republic of the Congo	","Congo (ex-Zaire)",paste(fishing_entity))
    )
  )

# The path
path_world <- paste(my_path("G"),"Spatial/SAU/SAU_Shapefile",sep="")

World_sf_df <- as.tibble(World_sf) %>% 
  select(sf_eez_name=eez_name,sf_objectid=OBJECTID,sf_eezid=EEZID)

# Vicky
Clean_sau_eez_fes_new <- Clean_sau_eez_fes %>% 
  left_join(UN_Regions) %>% 
  select(-`n()`) %>% 
  full_join(World_sf_df) %>% 
  select(1:3,4,8,9,everything())

#  Now check tim sau data
SAU_Tim_Data %>% 
  anti_join(Clean_sau_eez_fes_new) %>% 
  group_by(fishing_entity_id) %>% 
  summarise(n())

write_csv(Clean_sau_eez_fes_new,
          "matching_names.csv")

@@

Results_Path <- my_path("R")

@@

# Updates result's path for the jurisdiction
Results_Path <- paste(my_path("R"),Jurisdiction,"/",sep="")

# Species list to get species names
Exploited_Species <- fread(paste(my_path("D"),"Distribution/Species/exploited_species_list.csv",sep="")) %>% 
  clean_names()

Species_Sampled <- fread(paste(my_path("D"),"Distribution/Sampled_Species.csv", sep =""))

Spp_Clasification <- fread(paste(my_path("D"),"Distribution/Species/SppTaxonName.csv",sep="")) %>% 
  clean_names()

# Spatial Data needed to remove duplicates
sau_eez_fes <- fread(paste(my_path("G"),"Spatial/SAU/sau_eez_fes.csv",sep="")) %>% 
  clean_names()

Clean_sau_eez_fes <- sau_eez_fes %>% 
  gather("Type","fishing_region",2,4) %>% 
  left_join(sau_eez_fes,
            by = ("fishing_entity_id")
  ) %>% 
  group_by(eez_name,fishing_entity,fishing_entity_id) %>% 
  summarise(n()) %>% 
  ungroup() %>% 
  ### Manually Fix names for estimating catch
  mutate(eez_name = ifelse(eez_name =="Greece (without Crete)","Greece", # Vicky
                           ifelse(eez_name =="Greenland (Denmark)","Greenland",
                                  ifelse(eez_name =="United Kingdom (UK)","United Kingdom",
                                         ifelse(fishing_entity =="Italy","Italy",
                                                ifelse(eez_name =="Chile (mainland)","Chile",
                                                       ifelse(fishing_entity =="Brazil","Brazil",
                                                              ifelse(eez_name == "Ecuador (mainland)", "Ecuador",
                                                                     ifelse(eez_name =="Portugal (mainland)","Portugal",
                                                                            ifelse(fishing_entity == "Korea (North)","Korea (North)",
                                                                                   ifelse(fishing_entity == "Guadeloupe  (France)","Guadeloupe (France)",
                                                                                          ifelse(eez_name == "South Africa (Atlantic and Cape)","South Africa (Atlantic Coast)",
                                                                                          paste(eez_name)
                                                                                          )
                                                                                   )
                                                                            )
                                                       )))))))
                           ),
         fishing_entity = ifelse(fishing_entity == "Viet Nam","Vietnam",fishing_entity
         )
  )

# UN Regions dataset
UN_Regions <- read.csv(paste(my_path("D"),"Spatial/UN_Regions.csv",sep=""), header = TRUE) %>% 
  clean_names() %>% 
  # mutate(un_fishing_entity = country_or_area) %>% 
  group_by(#un_fishing_entity,
           fishing_entity = country_or_area,
           georegion = region_name,
           sub_region = sub_region_name) %>% 
  summarise(n=n()) %>% #merge china's 3 rows
  select(-n) %>% 
  filter(fishing_entity != "") %>%  # there are three rows with "developing" status as in, the code
  ungroup() %>% 
  # Change names to match SAU data and for shorter versions
  mutate(
    fishing_entity = gsub("\\s*\\([^\\)]+\\)","",fishing_entity),
    fishing_entity = gsub("Curaçao","Curacao",fishing_entity),
    fishing_entity = gsub("United Kingdom of Great Britain and Northern Ireland","United Kingdom",fishing_entity),
    fishing_entity = gsub( "United States of America", "USA",fishing_entity),
    fishing_entity = gsub("Democratic People's Republic of Korea", "Korea (North)",fishing_entity),
    fishing_entity = gsub("Republic of Korea", "Korea (South)",fishing_entity),
    fishing_entity = gsub("Iran (Islamic Republic of)", "Iran",fishing_entity),
    fishing_entity = gsub("Democratic Republic of the Congo", "Congo (ex-Zaire)",fishing_entity),
    # fishing_entity = gsub("Congo", "Congo, R. of",fishing_entity),
    fishing_entity = gsub("United Republic of Tanzania", "Tanzania",fishing_entity),
    fishing_entity = gsub("Cabo Verde", "Cape Verde",fishing_entity),
    fishing_entity = gsub("Timor-Leste", "Timor Leste",fishing_entity),
    fishing_entity = gsub(" and ", " & ",fishing_entity),
    # fishing_entity = gsub("Puerto Rico (USA)", "Puerto Rico",fishing_entity),
    fishing_entity = gsub("Taiwan", "Taiwan (China)",fishing_entity),
    fishing_entity = gsub("Côte d’Ivoire", "Côte d'Ivoire",fishing_entity),
    # fishing_entity = gsub("Russian Federation", "Russia",fishing_entity)
    fishing_entity = gsub("Viet Nam", "Vietnam",fishing_entity),
    fishing_entity = gsub("Solomon Islands", "Solomon Isl.",fishing_entity),
    fishing_entity = gsub("Marshall Islands", "Solomon Isl.",fishing_entity),
  ) %>% 
  mutate(
    fishing_entity = ifelse(fishing_entity == "Congo","Congo, R. of",
                            ifelse(fishing_entity == "Democratic Republic of the Congo	","Congo (ex-Zaire)",paste(fishing_entity))
                            )
  )

# Manually change congo
# UN_Regions[52,1] <- "Congo, R. of"

# Load Land shapefile
path_world_land <- paste(my_path("G"),"Spatial/ne_50m_admin_0_countries/ne_50m_admin_0_countries",sep="")

@@

# The path
path_world <- paste(my_path("G"),"Spatial/SAU/SAU_Shapefile",sep="")

@@

@@

# Read Sau Value Data (Thank you Tim!)
SAU_Tim_Data <- fread(paste(my_path("D"),"Distribution/sau_catch_value_country_taxon_JEPA.csv", sep =""))

@@

# Read Species Status Data (Sub-routine Species Status)
Status_Data <- fread(paste(my_path("R"),"EEZ/Species_Status.csv", sep ="")) %>% 
  clean_names() %>% 
  rename(sf_eez_name=territory)

@@

Clean_Results_Trans <- fread(paste(my_path("R"),"/EEZ/Clean_Results_Trans.csv", sep =""))
